\documentclass[11pt]{article}

\usepackage{graphicx}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in


\title{ Robert Soul\'{e} Career Summary}
\author{  }
\date{ }

\begin{document}

\maketitle	
\thispagestyle{empty}


Robert Soul\'{e} is a Tenured Associate Professor in the Department of
Computer Science at Yale University, with a joint appointment in the
Department of Electrical Engineering. He is a Senior Member of 
the ACM and IEEE.  Prior to joining Yale, he was an Associate
Professor in the Faculty of Informatics at the Universit\`{a} della
Svizzera italiana in Lugano, Switzerland.

%% His research interests are
%% broadly in computer systems, having made significant contributions
%% in computer networks, distributed systems, databases, operating systems,
%% and programming languages.

%where he still holds an Adjunct Professor position.


Professor Soul\'{e} is a leading computer networking researcher, well-known in the research community
for his work on software-defined networks (SDN). He is among the
top-five most cited authors from the Symposium of SDN Research (SOSR)
conference series. He is particularly recognized for his foundational
contributions to in-network computing. His seminal work on this topic has
been recognized with Best Paper awards at USENIX NSDI 2018, and ACM CoNEXT 2020,
as well as the 2019 ACM SIGMETRICS Highlights Beyond SIGMETRICS.


%% His work was among the first
%% to propose pushing traditional application logic into programmable
%% network switches, drawing
%% into question the long-standing assumptions about the division of
%% labor between applications and the network.

Professor Soul\'{e} made important contributions to the development of the P4
language, the Barefoot Tofino Programmable Switch Chip,
and the development of applications that used those
technologies. He led
the development team for Barefoot Networks (and later Intel)'s Deep
Insight Network telemetry system. He was a member of the
P4 Technical Steering Team and served as Chair of the P4 Education
Working Group. For his contributions to the Barefoot Tofino
Programmable Switch Chips and the P4 Programming Language, Professor
Soul\'{e} was a recipient of the 2025 ACM SIGCOMM Networking Systems
Award.

His recent work has focused on the environmental impact of computer networks
and distributed systems. He is Co-PI on a joint UK Engineering and
Physical Sciences Research Council (EPSRC) / US National Science Foundation (NSF) grant to study carbon-aware networking and the recipient of
a Yale University Planetary Solutions Acceleration Award for developing
an energy-proportional switch. He is particularly interested in exploring
the trade-offs in energy efficiency and fault-tolerance in distributed systems.

During his Ph.D. studies, Professor Soul\'{e} explored large-scale,
distributed stream processing. During this time, he was a co-op in the
Data Intensive Systems and Analytics at IBM T. J. Watson Research
Center, and his thesis work contributed to the SPL compiler for the
IBM Infosphere Streams stream processing engine. For this work,
Soul\'{e} received four IBM Invention Achievement Awards and an IBM
Invention Plateau Award. The Streams project was awarded an R\&D 100
Award For The Most Breakthrough Innovation.  His work on compiler
optimizations for streaming languages received the best paper award at
at ACM DEBS 2012.


%% His most recent work has focused on
%% energy-efficiency, the formal specification of quantum networks,
%% synchronous consensus protocols, and improving the observability
%% of operating system state.

Professor Soul\'{e} has authored more than 65 peer reviewed publications and is
an inventor on 11 US patents. He regularly serves on technical program committees for top systems
conferences, including NSDI, SIGCOMM, OSDI, and EuroSys. %He has
%organized three refereed tutorials at SIGCOMM and one at NSDI.


He has held consulting positions in industry at Barefoot Networks,
Intel Corporation, and most recently, Cerebras Systems, where he works
on the network architecture for their AI inference and training data
centers.  Prior to pursuing a career in academia, he worked at several
companies in industry, including Morgan Stanley, Bloomberg, and
LimeWire.

%% Notably, for a brief period of time, LimeWire was among the
%% most-downloaded applications on the Internet.


Professor Soul\'{e} received a Ph.D. from New York University and a
B.A. from Brown University. After completing his Ph.D., he was a
post-doctoral associate at Cornell University.








\end{document}
